\documentclass[10pt, a4paper, twocolumn]{book}
\usepackage{outback}

\title{\uppercase{Outback}}
\subtitle{An RPG system for the mad}
\author{Matt Brennan}
\date{}

\begin{document}
\frontmatter
\maketitle
\tableofcontents

\mainmatter
\chapter{Welcome to the wasteland}
It's a mad world out there. Food and water are scarce. Bullets and guzzoline
come cheap. 
\section{Playing the game}
When you undertake a difficult action, you make a die roll in one of your stats.
The roll will be contested by another roll, either by yourself, the GM, or
another player. Each of you rolls a \die{d20} and adds the modifier for that
stat. If your roll is greater than or equal the opposing roll, you succeed. Different tasks will have particular consequences for success and failure.

\subsection{Rolls for driving}
Vehicles have their own set of stats, which depend on how the vehicle is
outfitted, its condition \emph{et cetera}. When you perform a driving-related
task (for example manoeuvring, braking or ramming), your modifier for the roll
is your \stat{Driving} modifier plus the car's relevant modifier.

\subsection{Stats}
A stat is a number from 0 to 20 that describes your aptitude in a particular
skill or a facet of your vehicle's capability. The modifier for a stat is
given by the table below (or by subtracting 9 and dividing by 2, rounding
down).

\begin{wraptable}{l}{0.13\textwidth}
\vspace*{-10pt}
\begin{tabular}{cc}
  Stat  & Modifier \\
  \hline 
  0     & -5       \\
  1-2   & -4       \\
  3-4   & -3       \\
  5-6   & -2       \\
  7-8   & -1       \\
  9-10  &  0       \\
  11-12 & +1       \\
  13-14 & +2       \\
  15-16 & +3       \\
  17-18 & +4       \\
  19-20 & +5
\end{tabular}
\vspace*{-10pt}
\end{wraptable}

The stats for characters are \stat{Brawn}, \stat{Brains}, \stat{Armour}, \stat{Agility},
\stat{Driving} and \stat{Repair}. For vehicles, there's \stat{Speed},
\stat{Acceleration}, \stat{Braking}, \stat{Handling}, \stat{Ruggedness} and \stat{Weight}.

Depending on environmental conditions, injuries, wear \&
tear and other factors, there could be temporary modifiers that also apply to
rolls. For example, on rough terrain, \stat{Handling} rolls will have a penalty
of -2.

\chapter{Character Classes}
\section{Wheelman}
\section{Blackfinger}
\section{[weapons specialist name tbc]}
\chapter{Vehicle Customisation}
\chapter{Vehicular Combat}

\chapter{Melee Combat}
\end{document}