% !TEX root = ../../outback-basic-and-extended.tex

\let\s\stat
\let\xs\scriptsize

Exactly one of each part is required. Each part contributes to one or two stats of your vehicle: add together the numbers for each stat from each part. For example, to find your vehicle's \stat{Acceleration}, add the values from the Engine and Aspiration rows. A vehicle's \stat{Max HP} is 5 times its \stat{Ruggedness} plus 12. When creating a vehicle for a new character, it can cost at most 500 scrap.

{\small \begin{tabularx}{\linewidth}{rXccc}
             &                     & \small Basic & \small Improved & \small Finest \\
Part         & Stats               & \xs 20 scrap & \xs 50 scrap    & \xs 100 scrap \\
\hline%-------------------------------------------------------------------------------
Engine       & \s{Max speed}       & -1           & 0               & +1            \\
             & \s{Acceleration}    & -4           & 0               & +4            \\
Transmission & \s{Max speed}       & -4           & 0               & +4            \\
Aspiration   & \s{Acceleration}    & -1           & 0               & +1            \\
Tyres        & \s{Handling}        & -4           & 0               & +4            \\
             & \s{Braking}         & -1           & 0               & +1            \\
Suspension   & \s{Handling}        & -1           & 0               & +1            \\
Brakes       & \s{Braking}         & -4           & 0               & +4            \\
Chassis      & \s{Weight}          & -4           & 0               & +4            \\
             & \s{Ruggedness}      & -1           & 0               & +1            \\
Armour       & \s{Ruggedness}      & -4           & 0               & +4            \\
             & \s{Weight}          & -1           & 0               & +1            \\
\hline%-------------------------------------------------------------------------------
Fuel tank    & \s{Fuel difficulty} & +6           & +1              & -5            \\
             & \s{Weight}          & -1           & 0               & +2            \\
\end{tabularx}}

\begin{abstractsection}{Vehicle upgrades}
  When you have access to a garage, for example in a stronghold, you may upgrade your vehicle's parts. An upgrade takes a day to complete, and costs the difference between the old and new parts plus 20 scrap; for example, upgrading from \emph{Basic} to \emph{Finest} costs 100 scrap, or from \emph{Improved} to \emph{Finest} costs 70 scrap.
\end{abstractsection}

\begin{abstractsection}{Extra parts}
These parts don't replace the standard parts of your vehicle and provide extra capability or specialisation.

\begin{describe}{Bull horns}
  \prop{Cost}{50 scrap}
  \prop{Weight}{1}
  A pair of spiked bull bars to fit on the front grille of your vehicle. Your maximum damage for \emph{Shunt} and \emph{Ram} attacks increases by 10.
\end{describe}

\begin{describe}{Wheel spikes}
  \prop{Cost}{30 scrap}
  Barbs fitted to your wheel rims. When you succeed a \emph{Sideswipe} attack, the target makes an extra \stat{Ruggedness} roll versus your original attack score. If you succeed, the target is affected by a \emph{Blowout}.
\end{describe}

\begin{describe}{Nitrous boost}
  \prop{Cost}{100 scrap}
  A single-use tank of N\textsubscript{2}O. When used as an action, your vehicle's \stat{Speed} increases by \textbf{2} until the end of the setpiece.
\end{describe}

\end{abstractsection}
