% !TEX root = ../outback-basic-and-extended.tex

If you don't man\oe{}uvre in a tick, or you take a man\oe{}uvre that doesn't affect your speed, subtract 10 plus your vehicle's \stat{Weight} modifier from your speed.

\begin{describe}{Maintain speed}
  \prop{Fuel}{0}
  \prop{Cooldown}{\duration{\durationInstant{}}}
  Your \stat{Speed} doesn't change at the end of the tick.
\end{describe}

\begin{describe}{Accelerate}
  \prop{Fuel}{2}
  \prop{Cooldown}{\duration{\durationInstant{}}}
  Roll \die{2d8} plus half your \combined{\stat[Driving]{Wit}}{\stat{Acceleration}} modifier. Add the result to your \stat{Speed}.
\end{describe}

\begin{describe}{Brake}
  \prop{Fuel}{0}
  \prop{Cooldown}{\duration{\durationQuick{}}}
  Roll \die{2d8} plus half your \combined{\stat[Driving]{Wit}}{\stat{Braking}} modifier. Subtract the result from your \stat{Speed}.
\end{describe}

\begin{describe}{Handbrake}
  \prop{Fuel}{0}
  \prop{Cooldown}{\duration{\durationLong{}}}
  At the end of the tick, your Speed drops to 0.
\end{describe}

\begin{describe}{Evade}
  \prop{Fuel}{0}
  \prop{Cooldown}{\duration{\durationSlow{}}}
  During this man\oe{}uvre's cooldown, you may use \combined{\stat[Driving]{Wit}}{\stat{Handling}} as the skill to defend against any vehicular attack.
\end{describe}

\begin{describe}{Corner}
  \prop{Fuel}{0}
  \prop{Cooldown}{\duration{\durationInstant{}}}
  The GM will warn you 8 ticks before you will reach a bend in the road (at your current speed). Roll \combined{\stat[Driving]{Wit}}{\stat{Handling}} against the \stat{Difficulty} of the terrain when you reach the bend. If you succeed, you make it around the corner. If you fail (or do not take this man\oe{}uvre), you leave the road. Depending on the environment, you may continue off-road, become stuck, or hit an obstacle.
\end{describe}

\begin{abstractsection}{Collisions}
  When your vehicle collides with an obstacle, roll \stat{Speed} versus a single \die{d12}. If you ``succeed'', your vehicle takes damage equal to the difference. Your \stat{Speed} drops to 0. A collision has \duration{\durationSlow{}} cooldown, and you can't man\oe{}uvre this tick.
\end{abstractsection}
