% !TEX root = ../../outback-basic-and-extended.tex

\begin{describe}{Knuckle dusters}
  \prop{Cost}{30 scrap}
  While wearing these knuckle dusters, your unarmed attacks have a maximum damage of 20.
\end{describe}

\begin{describe}{Shiv}
  \prop{Cost}{5 scrap}
  Makeshift knife. Melee weapon with maximum damage of 5, or can be used to finish off an unconsious opponent without an attack roll.
\end{describe}

\begin{describe}{Combat knife}
  \prop{Cost}{80 scrap}
  That's not a knife... \emph{that's} a knife. Melee weapon with maximum damage of 15.
\end{describe}

\begin{describe}{Type 56 Carbine (with telescopic sight)}
  \prop{Cost}{160 scrap}
  \prop{Ammo capacity}{4}
  Rifle. Ranged weapon with maximum damage of 30. Can directly hit occupants of vehicles.
\end{describe}

\begin{describe}{Remington 870 sawn-off}
  \prop{Cost}{80 scrap}
  \prop{Ammo capacity}{6}
  12-gauge shotgun. Ranged weapon with maximum damage 20. You target up to three combatants close together; each combatant makes a separate defending roll.
\end{describe}

\begin{describe}{Heckler \& Koch MP5}
  \prop{Cost}{250 scrap}
  \prop{Ammo capacity}{16}
  Sub-machine gun. Ranged weapon with maximum damage 10. You make three shots in one action; make three attack rolls against a single target.
\end{describe}

\begin{describe}{Glock 17}
  \prop{Cost}{40 scrap}
  \prop{Ammo capacity}{10}
  Semiautomatic pistol. Ranged weapon with maximum damage 15. Can directly hit occupants of vehicles.
\end{describe}

\begin{describe}{Smith \& Wesson Model 29}
  \prop{Cost}{70 scrap}
  \prop{Ammo capacity}{6}
  Long-barrel revolver. Ranged weapon with maximum damage 25. Can directly hit occupants of vehicles.
\end{describe}

\hr

\begin{describe}{Crowbar}
  \prop{Cost}{20 scrap}
  Melee weapon, with maximum damage of 12. Can also be used to pry open containers, locked doors etc.. You make a \stat{\statPhysical} roll against the object's \stat{Ruggedness}.
\end{describe}

\begin{describe}{Blackthumb's tools}
  \prop{Cost}{100 scrap}
  A standard set of vehicle-repair tools, including a wrench that can be used as a melee weapon with a maximum damage of 10. Required to repair vehicle afflictions.
\end{describe}

\begin{describe}{Jerry can}
  \prop{Cost}{10 scrap}
  \prop{To fill}{50 scrap}
  A fuel canister that can contain 4 units of fuel.
\end{describe}

\begin{describe}{Spyglass}
  \prop{Cost}{100 scrap}
  You can use the spyglass to see long distances. Using the glass to survey increases your \stat{\statMental} by 1 for that roll.
\end{describe}

\begin{describe}{Cartographer's kit}
  \prop{Cost}{40 scrap}
  Using this kit, you can create a map of the vicinity. This takes 30 minutes. Using the map to navigate increases your \stat{\statMental} by 1 for that roll.
\end{describe}

\begin{describe}{History relic}
  \prop{Cost}{priceless}
  An old book, a handful of photos, a child's doll, etc.. Once in each combat, you can describe how the relic lets you cling to your long-forgotten past. Your \stat{\statSkill} increases by 1 until the end of the setpiece.
\end{describe}

\begin{describe}{Chrome spray}
  \prop{Cost}{10 scrap}
  Single-use spray. Your \stat{\statPhysical} increases by 1 until the end of the setpiece.
\end{describe}

\hr

\begin{describe}{Leathers}
  \prop{Cost}{80 scrap}
  Your \stat{\statSkill} increases by 1 for defence rolls versus unarmed and melee weapon attacks.
\end{describe}

\begin{describe}{Riot armour}
  \prop{Cost}{120 scrap}
  Your \stat{\statSkill} increases by 1 for defence rolls versus ranged weapon attacks.
\end{describe}
